\section{Future work}

One potential avenue for future work is to improve the decoding process for the predicted data from the SKEP model. In our current implementation, we found that the "aspect" attribute was None for all predicted data. This is an issue that needs to be addressed in the future, as the aspect information is critical for identifying the specific attributes that customers are mentioning in their reviews.

Another area for future work is to expand the dataset used for training and evaluation. While our current dataset provided a strong foundation for our sentiment analysis system, it is relatively small and limited to a specific domain. By expanding the dataset to include more diverse domains and languages, we can further improve the generalizability of our system and provide more comprehensive insights into customer opinions.

\section{Conclusion}

In conclusion, this project presents a structured sentiment analysis system based on the SKEP model, which is capable of extracting opinion pairs and identifying sentiment polarity for different attributes mentioned in customer reviews. We evaluated our system on a labeled dataset and achieved high accuracy in both opinion extraction and relation classification tasks.

Through this project, we have demonstrated the effectiveness of the SKEP model for structured sentiment analysis and provided valuable insights into customer opinions for businesses. However, there is still much work to be done in this area, including improving the decoding process and expanding the dataset for more diverse domains and languages.